### 2014-05-21 remy_eval.tex
Slight tweak to ellipse language

Ellipses that are narrower in the throughput or delay axis correspond
to protocols that are more consistent in allocating those
quantities. Protocols with large ellipses are those where
identically-positioned users differ widely in experience based on the
luck of the draw or the timing of their entry to the
network.\footnote{The ellipse represents the variability of the
  results for all nodes across all simulation runs. Thus, the notion
  of ``variability'' here includes both within-run variability or
  fairness (different results for different nodes that compete
  concurrently) as well as variability across runs. In practice, our
  100-second simulation runs were generally long enough, relative to flow
  durations, that the ellipse can be broadly interpreted as
  simply a measure of fairness.} The orientation of an ellipse
represents the {\em covariance between the throughput and delay}
measured for the protocol; if the throughput were uncorrelated with
the queueing delay (note that we show the queueing delay, not the
RTT), the ellipse's axes would be parallel to the graph's.  Because of
the variability and correlations between these quantities in practice,
we believe that such throughput-delay plots are an instructive way to
evaluate congestion-control protocols; they provide more information
than simply reporting mean throughput and delay values.

>>>>

Ellipses that are narrower in the throughput or delay axis correspond
to protocols that are more consistent in allocating those
quantities. Protocols with large ellipses are those where
identically-positioned users differ widely in experience based on the
luck of the draw or the timing of their entry to the
network.\footnote{The ellipse represents the variability of the
  results among all nodes across all simulation runs. Thus, the notion
  of ``variability'' here includes both within-run variability or
  fairness (differing results among nodes that compete
  concurrently) as well as variability across runs. For the most part, our
  100-second simulation runs were long enough, relative to flow
  durations, that the ellipses can broadly be interpreted as
  an indicator of fairness.} The orientation of an ellipse
represents the {\em covariance between the throughput and delay}
measured for the protocol; if the throughput were uncorrelated with
the queueing delay (note that we show the queueing delay, not the
RTT), the ellipse's axes would be parallel to the graph's.  Because of
the variability and correlations between these quantities in practice,
we believe that such throughput-delay plots are an instructive way to
evaluate congestion-control protocols; they provide more information
than simply reporting mean throughput and delay values.
